---
title: "week11-fifa.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)

```



## TidyTuesday --- Week 111

This is TidyTuesday for Week 11.

First, we load a bunch of libraries needed.

```{r setup-R}
## load libraries
library(tidyverse)
```

## Data

Then we get the data.
```{r data}
## getting the data
url <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/week11_fifa_audience.csv" ## click on "raw"
name <- "week11-fifa/week11_fifa_audience.csv"

## 1) from the 538 package
library(fivethirtyeight)
## apropos("fifa") ## find the fifa dataset in R from the 538 package
data1 <- fifa_audience

## 2) directly from github
data2 <- read_csv(url) 

## 3) download from github, then import through read_csv
download.file(url = url, destfile = name) ## download data
data3 <- read_csv(name) ## read data

## we'll go for the 3rd option
data <- data3

## little bit of tidying : remove the first column
data <- data %>% select(-1)

```

`?fifa_audience` we learn that the dataset is the raw data behind the story ["How To Break FIFA"](https://fivethirtyeight.com/features/how-to-break-fifa/) (3652?? rows).

The dataset represents each country as a row (`r data %>% select(country) %>% distinct() %>% nrow()` rows in total) and 4 features as columns:

- confederation
- population_share (percentage)
- tv_audience_share (percentage)
- gdp_weighted_share (percentage)

```{r summary-data}
library(skimr)
skim(data)

```

## Plots

Make a plot. Turn the data into the long format

```{r tidying-data}

data.long <- data %>% gather(type, share, -c(country, confederation)) %>% mutate(type = str_remove_all(type, "_share"))

```

```{r plots-facet, fig.height=5}

qp <- ggplot(data = data.long) + geom_density(aes(share, fill = confederation), color = NA, alpha=I(0.4)) + facet_grid(.~type)+theme_bw()

qp + scale_x_continuous(trans='log10') + xlab("log10(share)")

qp + coord_trans(x="log10")

qp + scale_x_log10()


```

```{r plots-pairs, fig.height=5}



```
